RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2014-08-18 manuscripts/manuscript.Rmd
fix reference typos

This paper has been written as a dynamic document 
[@Xiei_2013].  The reader may paste the code blocks
shown into their R terminal to follow along with the exmples shown.

@@

Here we illustrate this process using the example of stochastic character
mapping [@Huelsenbecki_2003]. A stochastic character map is simply
an annotation of the branches on a phylogeny, assigning each section
of each branch to a particular "state" (typically of a morphological
characteristic).

@@

Data archiving is increasingly required by journals in evolutionary biology and 
biodiversity (e.g. @Whitlock_2010).  The burden of preparing and submitting properly
annotated data to archives continues to be a significant barrier [@Tenopir_2011; @Stodden_2014],
and many phylogenetic trees upon which studies are based are inaccessible or lost 
to the research community [@Drew_2013].  `RNeXML` seeks to lower these barriers
by providing functions to immediately archive NeXML files in scientific repositories.

>>>>

This paper has been written as a dynamic document 
[@Xie_2013].  The reader may paste the code blocks
shown into their R terminal to follow along with the exmples shown.

@@

Here we illustrate this process using the example of stochastic character
mapping [@Huelsenbeck_2003]. A stochastic character map is simply
an annotation of the branches on a phylogeny, assigning each section
of each branch to a particular "state" (typically of a morphological
characteristic).

@@

Data archiving is increasingly required by journals in evolutionary biology and 
biodiversity (e.g. @Rausher_2010).  The burden of preparing and submitting properly
annotated data to archives continues to be a significant barrier [@Tenopir_2011; @Stodden_2014],
and many phylogenetic trees upon which studies are based are inaccessible or lost 
to the research community [@Drew_2013].  `RNeXML` seeks to lower these barriers
by providing functions to immediately archive NeXML files in scientific repositories.

### 2014-08-18 manuscripts/manuscript.tex
fix reference typos

This paper has been written as a dynamic document ({\textbf{???}}). The
reader may paste the code blocks shown into their R terminal to follow
along with the exmples shown.

@@

Here we illustrate this process using the example of stochastic
character mapping ({\textbf{???}}). A stochastic character map is simply
an annotation of the branches on a phylogeny, assigning each section of
each branch to a particular ``state'' (typically of a morphological
characteristic).

@@

Data archiving is increasingly required by journals in evolutionary
biology and biodiversity (e.g. ({\textbf{???}})). The burden of
preparing and submitting properly annotated data to archives continues
to be a significant barrier (Tenopir \emph{et al.} 2011; Stodden 2014),
and many phylogenetic trees upon which studies are based are
inaccessible or lost to the research community (Drew \emph{et al.}
2013). \texttt{RNeXML} seeks to lower these barriers by providing
functions to immediately archive NeXML files in scientific repositories.

@@

@@

@@

>>>>

This paper has been written as a dynamic document (Xie 2013). The reader
may paste the code blocks shown into their R terminal to follow along
with the exmples shown.

@@

Here we illustrate this process using the example of stochastic
character mapping (Huelsenbeck \emph{et al.} 2003). A stochastic
character map is simply an annotation of the branches on a phylogeny,
assigning each section of each branch to a particular ``state''
(typically of a morphological characteristic).

@@

Data archiving is increasingly required by journals in evolutionary
biology and biodiversity (e.g. Rausher et al. (2010)). The burden of
preparing and submitting properly annotated data to archives continues
to be a significant barrier (Tenopir \emph{et al.} 2011; Stodden 2014),
and many phylogenetic trees upon which studies are based are
inaccessible or lost to the research community (Drew \emph{et al.}
2013). \texttt{RNeXML} seeks to lower these barriers by providing
functions to immediately archive NeXML files in scientific repositories.

@@

Huelsenbeck, J.P., Nielsen, R. \& Bollback, J.P. (2003). Stochastic
mapping of morphological characters. \emph{Systematic Biology},
\textbf{52}, 131--158. Retrieved from
\url{http://dx.doi.org/10.1080/10635150390192780}

@@

Rausher, M.D., McPeek, M.A., Moore, A.J., Rieseberg, L. \& Whitlock,
M.C. (2010). Data archiving. \emph{Evolution}, \textbf{64}, 603--604.
Retrieved from \url{http://dx.doi.org/10.1111/j.1558-5646.2009.00940.x}

@@

Xie, Y. (2013). \emph{Dynamic documents with R and knitr}. Chapman;
Hall/CRC, Boca Raton, Florida. Retrieved from
\url{http://yihui.name/knitr/}
